The controlled choice design and private paternalism in pawnshop borrowing

### 2024-05-21 ECTA submission/donde_ecta.tex
ecta submission

% use option [draft] for initial submission
%            [final] for the prepublication
\documentclass[ecta,nameyear,final]{econsocart}
%
%\usepackage{}
\RequirePackage[colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue,pagebackref]{hyperref}

@@

\usepackage{booktabs}
\usepackage{multirow}
\usepackage{float}         
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{dsfont}
\usepackage{colortbl}
\usepackage{comment}
\usepackage{lscape}
\usepackage{subcaption}
\newtheorem{theorem}{Theorem}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{prop}[theorem]{Proposition} 
\newtheorem{cor}[theorem]{Corollary} 
\newtheorem{assumption}{Assumption} 
\newtheorem{lem}{Lemma}

@@

We apply this approach to an important and understudied context: pawnshop lending. 
Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For purposes of comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{There is a large literature showing that stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscilate around 15\% (\url{https://tinyurl.com/yc2x5bjf}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent. The fee serves as a reminder and a means of reinforcing the importance of these interim payments. In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm.

@@

Despite these large financial cost savings, only 11\% of borrowers in the choice arm choose commitment. 
%If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. 
Can the borrowers who did not choose commitment be those who simply don't need it? 
To answer this question, we carry out a detailed analysis of treatment effect heterogeneity.
%We address this question by sequentially imposing more structure on the problem. 
We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from the forced commitment and control arms, following \cite{fan2010sharp}. This approach imposes no assumptions beyond the experimental randomization. We find that \textit{at least} 23\% of borrowers benefit from commitment. This implies that there must be many borrowers in the choice arm who did not demand commitment despite their \emph{individual treatment effect} from (forced) commitment being positive. Next, we impose an exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it. In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract. This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}. \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.} 
It also has testable implications that we fail to reject in our empirical context.\footnote{See \ref{append:exclusion} for details.}
Under this restriction, the controlled choice design point identifies the TOT, TUT, ASG, ASB, and ASL effects described above.  Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR. On average, the borrowers who would \textit{not} choose commitment, would have faced substantially lower financial costs if they had. Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATE, using the Causal Random Forest algorithm of \cite{atheygrf}. We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the commitment contract. 
In short, it is extremely difficult to find identifiable groups of borrowers who are \emph{harmed} by commitment, even when restricting attention to those who would not choose it voluntarily. 
%while only 37\% of those who chose commitment have negative conditional TOT effects.
While targeting commitment products to those that benefit the most is a policy that appears attractive, in this context we find that the usable targeting variables have relatively weak predictive power and hence even our best random forest targeting only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).

@@

Our paper makes a number of contributions to the literature. First, we propose a way to use this three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{While \cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers. This difference is what allows our design to point identify the ASG and related quantities.} 
We further provide simple, regression-based estimators for each of these causal parameters, along with procedures for computing associated cluster-robust standard errors.\footnote{See \ref{append:randchoice} for details.} A companion STATA package provides easy-to-use commands that implement our estimators and standard errors. The controlled choice design could be useful in other experimental settings where the question of interest centers on the merits of paternalism, public or private, or the relationship between choice and treatment effects. One obvious example is the design of other financial contracts beyond pawn loans. Another is education, where teachers typically mandate quizzes, homework, and other commitment mechanisms to mitigate student procrastination \citep{Ariely}. 
We further contribute to a relatively small existing literature that sheds light on private paternalism. In the context of food choice, \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment. In contrast to their paper, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection. In the context of school choice, \cite{Walters} combines a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates. He finds that students who select into more effective schools have smaller treatment effects from attending than those who do not select in. In contrast, our approach point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject.

@@

Our study also speaks to recent research on the effects of payment frequency. While experiments in microfinance markets have \textit{not} shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{Murdoch}. These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our setting of high default. Second, we provide a deeper analysis of \textit{both} take-up and the efficacy of voluntary commitment mechanisms. A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}. Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and \textit{would not} choose it. This allows us to conduct a more rigorous and nuanced analysis of private paternalism.

@@

\noindent \textbf{Appraising and lending.} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash. No other collateral and no credit history checks are needed. The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e. a teller, see Figure \ref{PawnshopPicture}). The appraiser weighs the gold piece and runs tests on its purity. Based on these she assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client. The borrower signs a 2-page contract with the conditions of the loan and leaves with the cash.

\noindent \textbf{Contract.} Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period. The client could make payments at the branch at any time with no penalty for pre-payment. Under this status quo contract, there are no payment reminders or any other kind of interim contact between the lender and the borrower. If the client returns to pay the principal plus the accumulated interest within 105 days, she recovers her pawn, otherwise the pawnbroker keeps the piece \textit{and} any payments already made. Before the contract expires, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and the same piece as the original contract (38\% of borrowers renew at least once with a given pawn). This contract is standard in the industry.  Pawnshops make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non-defaulted loans, and by keeping the payments made on defaulted loans.

\noindent \textbf{Borrowers.} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.  This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a ``non-urgent expense''.  When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%).

\noindent \textbf{Many borrowers lose their pawn.} Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches (see Figure \ref{GoldBuyers}), (b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. 
%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

We define a borrower's financial cost as the total monetary outflow --in cash or pawn value-- from the borrower to the lender. This includes all payments the borrower made toward interest and fees, but also the net difference between the appraised value of the pawn and the loan amount (Value-Loan) in the event of default. When there is no default the borrower gets her pawn back and there is no loss of value for the borrower. Payments towards capital are considered a cost only when the borrower defaults, as she does not get reimbursed for these. Note however that when she does not default payments to capital are not an actual outflow, as they sum up to the value of the loan the lender disbursed in the first place. The formula for financial cost for person $i$ is thus as follows: %\footnote{We alternatively defined financial cost as $\text{Financial Cost}_i = \sum_t P^I_{it} + \sum_t P^F_{it} + \sum_t P^C_{it} + \mathds{1}(\text{Default}_i) \times (\text{Value}_i)-\text{Loan}_i$, and obtained similar results.}:
\begin{align*}
    \text{Financial Cost}_i =&  \sum_t P^I_{it} +\sum_t P^F_{it}  
     + \mathds{1}(\text{Default}_i) \times (\text{Value}_i-\text{Loan}_i + \sum_t P^c_{it})
\end{align*}

\noindent where $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting. Because the period of the loan is only 90 days we do not apply discounting in calculating costs.  In robustness checks reported below we show that our results are virtually unchanged when applying a wide range of time discounting factors.

@@

As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account the entire loan period, including extensions of the loan through refinancing.} The standard definition is given in the following formula:
\begin{align*}
    (\text{APR})_i =&\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 
\end{align*}

\begin{figure}
    \begin{center}
    \begin{subfigure}{.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{Figuras/hist_fc.pdf}
        \caption{}
    \end{subfigure}
     \begin{subfigure}{0.45\textwidth}
       \centering
      \includegraphics[width=\textwidth]{Figuras/hist_apr.pdf}
      \caption{}
    \end{subfigure}
    \end{center}
 \caption{Financial cost. Panel (a) presents a histogram of financial cost for the control group. The figure plots separately the financial cost separately for borrowers who lose the pawn (blue) and those that recover it (transparent).  Panel (b) is analogous but displays the APR.}
     \label{fc_hist}
      %\footnotesize{ } \textit{Do file: }  \texttt{hist\_fc.do}
\end{figure}

Figure \ref{fc_hist}(a) plots a histogram of this financial cost in pesos for all loans in the experiment, stratified by whether we observed that they ended in default or recovery of the pawn. Figure \ref{fc_hist}(b) shows the analogous histogram for the APR.
%defaulted (44\%), recovered their pawn (43\%), or whether they are censored in our data (13\%). 
We see that borrowers who default incur higher costs; part of this is mechanical as losing their collateral is part of the cost. Most of the APR costs indeed come from clients who do not recover their pawn.
%The second thing to note is that those that are not closed at the end of our sample period have already incurred substantial financial cost, even though they have not defaulted yet.

%Of those who renew, 83\% lose the pawn. Figure \ref{fc_hist}(a) suggest that financial cost is significant, even for those that do recover their pawn. Panel (b) normalizes the cost by loan size. It shows that as a percentage of their pawn, most of the cost comes from clients that do not recover their pawn. For them the cost is between 140\% and 250\% of the loan value. %{The difference between panel (a) and (b) arises since clients who lose their pawn tend to be those that pledge cheaper pieces.}

@@

\subsection{Treatment arms and randomization}

\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.  It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, the same loan size/collateral ratio (70\%), and the same loan term (90 days, and a grace period of 15 days). Borrowers' gold pawns are appraised in the same way by the same appraisers under both the new and status quo contracts. The commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments. %\textcolor{red}{The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee.} 
The fee was modest and intended to make the payment deadlines salient. As a benchmark, the transportation cost to visit the branch to make a payment is comparable to the fee, on average.
%\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. 
%In contrast with \cite{John} we don't let the clients choose the size of the fee. \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}

@@

\noindent \textbf{Treatment Arms.} Treatments were randomized at the branch-day level. Each day a computer randomly assigned which types of contracts were on offer that day in the branch, and the IT system would only offer these.  We have 3 different experimental arms\footnote{The experiment included other independent arms that involved no fee penalties and did not emphasize the structure of payments. These are being analyzed in a separate paper.}

@@

\begin{figure}     
\begin{center}
\begin{subfigure}{\textwidth}
        \includegraphics[width=\textwidth]{Figuras/consort.pdf}
    \end{subfigure}
  \end{center}
 \caption{Experiment description}
     \label{exp_description}
%\textit{Do file: }  \texttt{ss\_att.do}
\end{figure}

\vspace{.2in}
\noindent \textbf{Randomization.}  We implemented the experiment in 6 branches of Lender $P$ beginning on September 6, 2012. The branches were selected by Lender $P$ to be dispersed across Mexico City and have varying sizes. In four of them the experiment ran for 102 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size. %Thus we eliminated {the smallest} ones. 
Branches are more than 5 km apart from each other, and there is no substitution among them; none of the consumers appear in more than one of our branches.

@@

\noindent \textbf{Timeline.} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments. For loans made in the first week of the experiment, we observe up to 338 subsequent days of loan information; for loans made in the last week we observe up to 235 days. Figure \ref{exp_description} also illustrates the number branch-days per arm, the number of loans, and the number of surveys. %Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them. There were two reasons: \hl{XXX}.

>>>>

% use option [draft] for initial submission
%            [final] for the prepublication
\documentclass[ecta,nameyear,draft]{econsocart}
%\documentclass[]{econsocart}
%
%\usepackage{}
\RequirePackage[colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue,pagebackref]{hyperref}

@@

\usepackage{booktabs}
\usepackage{multirow}
\usepackage{float}         
\usepackage{amsmath}
\usepackage{amscd}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{dsfont}
\usepackage{colortbl}
\usepackage{comment}
\usepackage{lscape}
\usepackage{subcaption}
\newtheorem{theorem}{Theorem}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{prop}[theorem]{Proposition} 
\newtheorem{cor}[theorem]{Corollary} 
\newtheorem{assumption}{Assumption} 
\newtheorem{lem}{Lemma} 
\usepackage{enumerate}

@@

We apply this approach to an important and understudied context: pawnshop lending. 
Pawn loans constitute one of the oldest and most prevalent forms of borrowing \citep{carter2012pawnshops}.
Our partner lender, for example, made over 4 million loans to more than a million clients during the past three years.\footnote{For comparison, there were 2.3 million microfinance clients in Mexico in 2009 \citep{Pedroza:2010}.} 
The question of choice versus paternalism is particularly salient in this context, as choice mistakes could arise from borrowers' low education and the fact that they typically borrow for emergencies under significant stress.\footnote{A large literature shows  stress impairs cognitive function, e.g. \cite{StressReview}.}
%\footnote{There are more than 11,000 pawn shops across the US, with 30 million clients and \$14 billion yearly revenues (in China it is a \$43 billion industry).  \url{https://tinyurl.com/ybm56dpe}, \url{https://tinyurl.com/y9zdcgws}, \url{https://tinyurl.com/y59ptdam}.}
Our experiment covers just under 5,000 pawnshop clients in 6 of our partner lender's Mexico City branches. Our control arm illustrates the costs of the status quo contract: fully \emph{44\%} of borrowers default, losing lose their pawn along with any payments made towards principal.\footnote{High pawn default rates are common, in the US they oscillate around 15\% (see \href{https://tinyurl.com/yc2x5bjf}{here}).} Our ``commitment choice'' arm gives borrowers the chance to opt into a structured repayment contract when taking a loan. The structured contract requires borrowers to make three monthly payments rather than one balloon payment at the end, with each monthly payment including the accrued interest at that time as well as a nominal fee of 2\% of that month's payment if the payment is delinquent. The fee serves as a reminder and a means of reinforcing the importance of these interim payments. In our ``forced commitment'' arm all borrowers are \emph{required} to repay using the same structured monthly contract offered on an opt-in basis in the commitment choice arm.

@@

Despite these large financial cost savings, only 11\% of borrowers in the choice arm choose commitment. 
%If the effect of commitment were homogeneous, this would be enough to conclude that the 89\% who did not choose it would have been financially better off if they had. However, we test and reject the null hypothesis of homogeneous treatment effects using the method of \cite{chernozhukov2018generic}. 
Can the borrowers who did not choose commitment be those who simply don't need it? 
To answer this question, we carry out a detailed analysis of treatment effect heterogeneity.
%We address this question by sequentially imposing more structure on the problem. 
We begin by bounding the distribution of individual treatment effects using the marginal outcome distributions from the forced commitment and control arms, following \cite{fan2010sharp}. This approach imposes no assumptions beyond the experimental randomization. We find that \textit{at least} 23\% of borrowers benefit from commitment. This implies that there must be many borrowers in the choice arm who did not demand commitment despite their \emph{individual treatment effect} from (forced) commitment being positive. Next, we impose an exclusion restriction positing that the effect of a given contract does not depend on \emph{how} borrowers obtain it. In other words, we assume that choosing a contract results in the same potential outcome as being assigned that contract. This is a relatively common if often implicit assumption in causal inference.\footnote{Papers that use variation in compulsory schooling laws to identify the returns to schooling, for example, typically interpret their results as the causal effect of additional \emph{education} rather than additional \emph{forced education}. \cite{chamberlain2011bayesian} uses a closely related assumption to develop a theory of optimal treatment choice.} 
It also has testable implications that we fail to reject in our empirical context.\footnote{See \autoref{sec:testing_exclusion} for details.}
Under this restriction, the controlled choice design point identifies the TOT, TUT, ASG, ASB, and ASL effects described above.  Our estimated TUT effect on financial cost savings is large: \$192 pesos, equivalent to a 10.6 percentage point savings in APR. On average, the borrowers who would \textit{not} choose commitment, would have faced substantially lower financial costs if they had. Finally, we combine our experimental treatment and outcome data with survey responses collected for a subset of borrowers to estimate conditional average treatment effects, both TUTs and ATE, using the Causal Random Forest algorithm of \cite{atheygrf}. We estimate positive conditional average TUT effects for 93\% of the borrowers who did \textit{not} choose the commitment contract. 
In short, it is extremely difficult to find identifiable groups of borrowers who are \emph{harmed} by commitment, even when restricting attention to those who would not choose it voluntarily. 
%while only 37\% of those who chose commitment have negative conditional TOT effects.
While targeting commitment products to those that benefit the most is a policy that appears attractive, in this context we find that the usable targeting variables have relatively weak predictive power and hence even our best random forest targeting only reduces the overall mis-targeting rate from 9.7\% (all to Forcing) to 9.5\% (our best-case feasible targeting mechanism).

@@

Our paper makes a number of contributions to the literature. First, we propose a way to use this three-armed experimental structure to recover treatment effects for choosers and non-choosers under minimal assumptions.\footnote{While \cite{fowlie2021default} likewise employ a three-armed experimental design in their study of the effect of electricity pricing, they identified \emph{two} TOT effects for different groups of ``treated'' households, whereas we simultaneously identify the TOT and TUT effects defined with respect to a single ``treated'' group of borrowers. This difference is what allows our design to point identify the ASG and related quantities.} 
A companion STATA package provides simple, regression-based estimators for each of these causal parameters, along with appropriate cluster-robust standard errors.\footnote{See \autoref{sec:estimation_inference} for details.} 
The controlled choice design could be useful in other experimental settings where the question of interest centers on the merits of paternalism, public or private, or the relationship between choice and treatment effects. One obvious example is the design of other financial contracts beyond pawn loans. Another is education, where teachers typically mandate quizzes, homework, and other commitment mechanisms to mitigate student procrastination \citep{Ariely}. 
We further contribute to a relatively small existing literature that sheds light on private paternalism. In the context of food choice, \cite{Sprenger} show that individuals with the most time-inconsistent preferences are actually least likely to demand commitment. In contrast to their paper, we directly identify the TUT, obviating the need to first elicit preferences before testing for negative selection. In the context of school choice, \cite{Walters} combines a distance instrument with additional structural assumptions, obtaining model-based TUT and ATE estimates. He finds that students who select into more effective schools have smaller treatment effects from attending than those who do not select in. In contrast, our approach point identifies TUT and TOT and a range of other interesting causal parameters without the need for a structural model, relying instead on relatively weak exclusion restrictions whose testable implications we fail to reject.

@@

Our study also speaks to recent research on the effects of payment frequency. While experiments in microfinance markets have \textit{not} shown the same benefits from providing a more regularized repayment environment as we find here \citep{Pande, barboni2023flexible}, these experiments differ from ours in two important ways: they are performed on top of already highly structured micro-finance contracts, and they involve borrower pools who may have selected into that type of lending precisely because it provides structure \cite{bauer2012behavioral}. These differences may explain why \citep{Pande} finds almost no default in the control group, in stark contrast to our setting of high default. Second, we provide a deeper analysis of \textit{both} take-up and the efficacy of voluntary commitment mechanisms. A number of papers have found low demand for commitment as we do.\footnote{\cite{Ashraf}, \cite{Gine}, \cite{Ted}, \cite{Royer}, \cite{Sprenger}. Others have found more robust demand for commitment (\cite{Kremer},  \cite{Casaburi}, \cite{Alcohol}, \cite{AprajitP&P}, \cite{Pascaline}).} Unlike all of these papers, however, we separately point-identify and estimate the effects of commitment for borrowers who would and \textit{would not} choose it. This allows us to conduct a more rigorous and nuanced analysis of private paternalism.

@@

%\hfill \newline
%\noindent \textbf{Appraising and lending.} 
\paragraph*{Appraising and Lending} Lender P takes gold jewelry as collateral in exchange for a fraction of the value of the piece, in cash. No other collateral and no credit history checks are needed. The transaction takes less than 10 minutes and is conducted at the branch in person between the client and the appraiser (i.e. a teller).
%, see Figure \ref{PawnshopPicture}). 
The appraiser weighs the gold piece and runs tests on its purity. Based on these she assigns a gold value to the piece, stores it as collateral, and gives 70\% of the gold value of the piece in cash to the client. The borrower signs a 2-page contract with the conditions of the loan and leaves with the cash.

%\hfill \newline
%\noindent \textbf{Contract.} 
\paragraph*{Contract} Lender P had only one type of contract, henceforth the \textit{status quo} contract. It stipulated that the interest rate was 7\% \textit{per month} compounded daily on the outstanding amount of the loan. The loan had a 90 days term with 15 days' grace period. The client could make payments at the branch at any time with no penalty for pre-payment. Under this status quo contract, there are no payment reminders or any other kind of interim contact between the lender and the borrower. If the client returns to pay the principal plus the accumulated interest within 105 days, she recovers her pawn, otherwise the pawnbroker keeps the piece \textit{and} any payments already made. Before the contract expires, the client had the right to renew for another 3 months by going to the pawnshop, paying the accumulated interest, and signing a new contract with exactly the same terms and the same piece as the original contract (38\% of borrowers renew at least once with a given pawn). This contract is standard in the industry.  Pawnshops make money in three ways: by reselling the jewelry left as collateral on defaulted loans, by charging interest on non-defaulted loans, and by keeping the payments made on defaulted loans.

%\hfill \newline
%\noindent \textbf{Borrowers.} 
\paragraph*{Borrowers} The clients that pawned understood these terms well (as we verified in interviews).\footnote{87\% of clients report in our survey that they have pawned before.} These clients have little or no access to other types of loans and they value the convenience of pawn borrowing.  This population of pawn borrowers is economically vulnerable:  30\% of them could not pay either water, electricity \& gas or rent in the past 6 months; 89\% said they are pawning because of an emergency, and only 12\% stated it was to use in a ``non-urgent expense''.  When asked why they are pawning this piece, 5\% responded ``lost a family member'', ``a medical emergency'' (11\%), or ``an urgent expense'' (72\%).

%\hfill \newline
%\noindent \textbf{Many borrowers lose their pawn.} 
\paragraph*{Many borrowers lose their pawn.}
Our context is also one with high borrower default: 43\% of clients lose their pawn in a time span of 230 days from the date of pawning. One potential explanation for high default is that clients are really just knowingly selling their gold piece through a pawn contract on which they intend to default. This appears unlikely for several reasons: (a) clients can easily sell the gold and obtain a higher amount of instant cash at gold-buying stores located close to almost all our pawnshop branches,
%(see Figure \ref{GoldBuyers})
(b) the reported subjective value of the pawn is larger than the appraised value for 83\% of clients, (c) among those that lose their pawn, 29\% paid a positive amount towards its recovery and on average paid 42\% of the value of their loan (see Figure \ref{proxy_naive} in Appendix) --- this can only be rationalized if they expected to recover their pawn, and (d) 72\% of borrowers report a 100\% probability of repaying their loan (and 98\% at least a 50\% chance of repaying) in our baseline survey at the time they take the loan.  %Note that high default could be detrimental from the lender's point of view, since it may reduce the likelihood that the client becomes a return customer. 
%Lender P was in fact explicitly interested in partnering with us to investigate how to reduce loan default, customer satisfaction, and repeat borrowing.

@@

We define a borrower's financial cost as the total monetary outflow --in cash or pawn value-- from the borrower to the lender. This includes all payments the borrower made toward interest and fees, but also the net difference between the appraised value of the pawn and the loan amount (Value-Loan) in the event of default. When there is no default the borrower gets her pawn back and there is no loss of value for the borrower. Payments towards capital are considered a cost only when the borrower defaults, as she does not get reimbursed for these. Note however that when she does not default payments to capital are not an actual outflow, as they sum up to the value of the loan the lender disbursed in the first place. The formula for financial cost for person $i$ is thus as follows: %\footnote{We alternatively defined financial cost as $\text{Financial Cost}_i = \sum_t P^I_{it} + \sum_t P^F_{it} + \sum_t P^C_{it} + \mathds{1}(\text{Default}_i) \times (\text{Value}_i)-\text{Loan}_i$, and obtained similar results.}:
\begin{align*}
    \text{Financial Cost}_i =&  \sum_t P^I_{it} +\sum_t P^F_{it}  
     + \mathds{1}(\text{Default}_i) \times \left(\text{Value}_i-\text{Loan}_i + \sum_t P^c_{it}\right)
\end{align*}
where $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting. Because the period of the loan is only 90 days we do not apply discounting in calculating costs.  In robustness checks reported below we show that our results are virtually unchanged when applying a wide range of time discounting factors.

@@

As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs. The standard definition is given in the following formula: $(\text{APR})_i =\left( 1 + \frac{\frac{\text{Financial Cost}_i}{\text{Loan}_i}}{\text{loan term}_i}\right)^{\text{loan term}_i}-1 $

@@

%\hfill \newline
\subsection{Treatment arms and randomization}

%\hfill \newline
%\noindent \textbf{The Commitment Contract.} 
\paragraph*{The Commitment Contract} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the design of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.  It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, the same loan size/collateral ratio (70\%), and the same loan term (90 days, and a grace period of 15 days). Borrowers' gold pawns are appraised in the same way by the same appraisers under both the new and status quo contracts. The commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was made salient in the contract and payment receipts, and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments. %\textcolor{red}{The idea that the fee itself is not driving the treatment is reinforced later in the paper where we show financial benefits many times larger than the fee, as well as treatment effects even on those who would fail to recover pawns and hence not pay the fee.} 
The fee was modest and intended to make the payment deadlines salient. As a benchmark, the transportation cost to visit the branch to make a payment is comparable to the fee, on average.
%\footnote{%The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. 
%In contrast with \cite{John} we don't let the clients choose the size of the fee. \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.}

@@

%\hfill \newline
%\noindent \textbf{Treatment Arms.} 
\paragraph*{Treatment Arms} 
Treatments were randomized at the branch-day level. Each day a computer randomly assigned which types of contracts were on offer that day in the branch, and the IT system would only offer these.  We have 3 different experimental arms\footnote{The experiment included other independent arms that involved no fee penalties and did not emphasize the structure of payments. These are being analyzed in a separate paper.}

@@

\begin{figure}[htbp]    
\begin{center}
\includegraphics[width=0.9\textwidth]{Figuras/consort.pdf}
  \end{center}
 \caption{Experiment description}
     \label{exp_description}
%\textit{Do file: }  \texttt{ss\_att.do}
\end{figure}

%\hfill \newline
%\noindent \textbf{Randomization.}  
\paragraph*{Randomization} We implemented the experiment in 6 branches of Lender $P$ beginning on September 6, 2012. The branches were selected by Lender $P$ to be dispersed across Mexico City and have varying sizes. In four of them the experiment ran for 102 days, and in 2 of them we ran it for a shorter time to economize on data collection costs once we realized we would not be constrained by sample size. %Thus we eliminated {the smallest} ones. 
Branches are more than 5 km apart from each other, and there is no substitution among them; none of the consumers appear in more than one of our branches.

@@

%\hfill \newline
%\noindent \textbf{Timeline.} 
\paragraph*{Timeline} Figure \ref{exp_description} shows the experimental timeline along with the length of time for which we observe payments. For loans made in the first week of the experiment, we observe up to 338 subsequent days of loan information; for loans made in the last week we observe up to 235 days. Figure \ref{exp_description} also illustrates the number branch-days per arm, the number of loans, and the number of surveys. %Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them. There were two reasons: \hl{XXX}.
